Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2023-04-10 results.tex
Adding DOFs and Computer SPEC

All runs were done on XX computer with YY specifications.

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
&Mesh size & $\Delta G_{solv}$\\
&\AA       &  kcal/mol \\
\hline
\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -107.6186 \\ 
& 0.39$\times$0.39$\times$0.39 & -107.8752\\ 
&0.26$\times$0.26$\times$0.26 & -108.3378\\ 
&0.195$\times$0.195$\times$0.195 & -108.5837\\ 
&0.098$\times$0.098$\times$0.098 & -108.8844\\ 
\hline
&Mesh dens. & \\
&vert/\AA$^2$ & \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 4.1 & -109.933 \\
FEM-BEM    & 6.7  & -110.238 \\
coupling    & 8.57  & -109.658 \\
    & 17 & -109.368 \\
    & 24.5 & -109.286 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
%    & 2 & -34.670\\
%Hybrid    & 4  & -33.603 \\
%FEM-BEM    & 8  & -32.822 \\
%    & 16 & -32.072 \\
%\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS. The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh. Add performance result?}
\label{table:arg2_variable}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{c|c|c|c|c|c|c}
Molecule & Mesh size  & $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
& vert/\AA$^2$ &  kcal/mol & & sec & sec & sec \\
\hline
 1pgb &  & -300.888 & 826 & 82 & 547 & 629  \\
 1lyz &  & -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
 1lyz gs3 & & -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
 1uxu &  & -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
 1igt &  &  -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
 \hline
\end{tabular}
\caption{Large tests' results}
\label{table:large_variable}
\end{table}

>>>>

All runs were done on Lenovo ThinkStation P620 with AMD Ryzen ThreadRipper PRO 3975WX 32-core 3.5 GHz and 128 GB RAM.

@@

\begin{table}
\centering
\begin{tabular}{c|c|c|c}
&Mesh size  & Grid points? & $\Delta G_{solv}$\\
&\AA       & &  kcal/mol \\
\hline
\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 &  & -107.6186 \\ 
& 0.39$\times$0.39$\times$0.39 & & -107.8752\\ 
&0.26$\times$0.26$\times$0.26 & & -108.3378\\ 
&0.195$\times$0.195$\times$0.195 & & -108.5837\\ 
&0.098$\times$0.098$\times$0.098 & & -108.8844\\ 
\hline
&Mesh dens. & DOFs & $\Delta G_{solv}$\\
&vert/\AA$^2$   &  &  kcal/mol \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 4.1 & 3 491 & -109.933 \\
FEM-BEM    & 6.7  & 5 787 & -110.238 \\
coupling    & 8.57  & 8 844 & -109.658 \\
    & 17 & 19 911 & -109.368 \\
    & 24.5 & 32 302 & -109.286 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
%    & 2 & -34.670\\
%Hybrid    & 4  & -33.603 \\
%FEM-BEM    & 8  & -32.822 \\
%    & 16 & -32.072 \\
%\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS. The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh. Add performance result?}
\label{table:arg2_variable}
\end{table}

@@

\begin{table}
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c}
Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
& DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
\hline
 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
 1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
 1uxu & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
 1igt & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
 \hline
\end{tabular}}
\caption{Large tests' results}
\label{table:large_variable}
\end{table}
%
%\begin{table}
%\centering
%\begin{tabular}{c|c|c|c|c|c|c|c|c}
%Molecule & Mesh size  & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
%& vert/\AA$^2$ & DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
%\hline
% 1pgb &  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
% 1lyz &  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
% 1lyz gs3 &  & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
% 1uxu &  & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
% 1igt &  & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
% \hline
%\end{tabular}
%\caption{Large tests' results}
%\label{table:large_variable}
%\end{table}
